Time-series modeling of epidemics in complex populations: detecting changes in incidence volatility over time

### 2025-01-24 ms-3/ms.tex
Update ms.tex
Finish new app to sim data

Our simulation samples start points and theta values, and incidence is modeled according to overall incidence trends.

>>>>

To test the fidelity of our $\theta$ estimates and the validity and power of our LRT, we simulated epidemic curves spanning 16 time steps each. Our simulation framework samples the start point of each curve and a $\theta$ value on each side of the midpoint. Incidence modeled according to overall incidence trends ((Fig\ 1 a) is scaled by the population size for that curve (population sizes used ranged from $10^3$ to $10^7$). Equal $\theta$ values on both sides of the midpoint were set for 10% of the epidemic curves. The estimation framework and LRT was applied to each epidemic curve in the simulated data in order to produce estimates of $\theta$ on either side of the midpoint, as well as a p-value from the LRT. This approach allowed us to test the robustness of our framework over a range of $\theta$ difference magnitudes, underlying population sizes, and point of the epidemic curve at which the procedure is applied.
